---
title: 'Phase 1: Survey Objects'
author: "Isabel Arvelo"
date: "2022-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(survey)
library(ggsurvey)
options( survey.lonely.psu = "adjust" )
```


**NSDUH**

```{r}
NSDUH_Phase1 <- readRDS("Phase0_NSDUH.rds")
```

```{r}
#Adult Subset 
NSDUH_Phase1_adults <- NSDUH_Phase1[NSDUH_Phase1$catage > 1, ]
```

```{r}
#Adult Survey Object
NSDUH_survey_adults <- svydesign(id = ~verep, strata = ~VESTRQ1Q4_C, nest = TRUE, weights = ~ANALWTQ1Q4_C, data = NSDUH_Phase1_adults)
```

```{r}
#All Obs Survey Object 
NSDUH_survey <- svydesign(id = ~verep, strata = ~VESTRQ1Q4_C, nest = TRUE, weights = ~ANALWTQ1Q4_C, data = NSDUH_Phase1)
```

```{r}
#This variable can be used to calculate unweighted and weighted population sizes
NSDUH_survey<-	update(one = 1 ,	NSDUH_survey)
NSDUH_survey_adults <-	update(one = 1 ,	NSDUH_survey_adults)
```


```{r}
unwtd.count( ~one , NSDUH_survey )							# total valid cases
svyby( ~one , ~catage , NSDUH_survey , unwtd.count )		# by age group
svyby( ~one , ~irsex , NSDUH_survey , unwtd.count )		# by sex
svyby( ~one , ~NEWRACE2 , NSDUH_survey , unwtd.count )		# by race/ethnicity
```

```{r}
svyby( ~one , ~MHSUTK_U , NSDUH_survey_adults , unwtd.count )
```


```{r}
#Weighted Counts - matches published numbers 
svytotal( ~one ,NSDUH_survey )							     # total valid cases
svyby( ~one , ~catage , NSDUH_survey , svytotal )			# by age group
svyby( ~one , ~irsex , NSDUH_survey, svytotal )			# by sex
svyby( ~one , ~NEWRACE2 , NSDUH_survey, svytotal )		# by race/ethnicity
```


```{r}
svymean(~MHSUTK_U , NSDUH_survey_adults)	
```

```{r}
svymean(~spdmon , NSDUH_survey_adults)	
```

```{r}
save(NSDUH_survey_adults, file = "~/NSDUH_survey_adults.RData")
save(NSDUH_survey, file = "~/NSDUH_survey.RData")
```

```{r}
save(NSDUH_survey_adults, file = "~/Desktop/Independent Study/PrelimApp/data/NSDUH_survey_adults.RData")
```




#BRFSS 

```{r}
BRFSS_Phase1 <- readRDS("Phase0_BRFSS_Survey.rds")

BRFSS_Phase1 <- BRFSS_Phase1 %>% rename(ststr = '_STSTR')  %>% rename(llcpwt = '_LLCPWT')
```

```{r}
BRFSS_survey_all <- svydesign(id = ~1, 
                              strata = ~ststr, 
                              weights = ~llcpwt, 
                              data = BRFSS_Phase1)
```



```{r}
BRFSS_survey_all$variables <- BRFSS_survey_all$variables %>%
                                  rename( X_STATE = "_STATE", 
                                          IMPRACE = "_IMPRACE", 
                                          AGE_G = "_AGE_G", 
                                          EDUCAG = "_EDUCAG", 
                                          HLTHPLN = "_HLTHPLN")

```



```{r}
save(BRFSS_survey_all, file = "~/Desktop/Independent Study/PrelimApp/data/BRFSS_survey_all.RData")
```









**Attempting Raking** 

margins 6 and 7 were collapsed

Race/ethnicity in margin 6 was collapsed to non-Hispanic White and Other for males; non-Hispanic White, non-Hispanic Black, and Other for females. In margin seven, race/ethnicity was collapsed to non-Hispanic White and Other.

1: Sex by Age - ACS Data 
2: Race/Ethnicity - ACS data 
3: Education: five-year American Community Survey PUMS dataset 
4: Marital Status: five-year American Community Survey PUMS dataset 
5: Home Ownership: five-year American Community Survey PUMS dataset 
6: Sex by Race/Ethnicity (collapsed categories)
7: Race/Ethnicity by Age (collapsed categories) - 
8: Phone Usage - Would require webscraping from National Center for Health Statistics


**NHIS**

```{r}
NHIS_Adult_Phase1 <- readRDS("Phase0_NHIS_Adult.rds")
NHIS_Child_Phase1 <- readRDS("Phase0_NHIS_Child.rds")
```

```{r}
NHIS_Adult_Phase1 <- NHIS_Adult_Phase1 %>% rename(wtfa = 'WTFA_A') 
NHIS_Child_Phase1 <- NHIS_Child_Phase1 %>% rename(wtfa = 'WTFA_C') 
```


```{r}
NHIS_Adult_Survey_All <- svydesign(id= ~PPSU, 
                                   strata = ~PSTRAT, 
                                   nest = TRUE, 
                                   weights = ~wtfa, 
                                   data = NHIS_Adult_Phase1)
```


```{r}
NHIS_Child_Survey_All <- svydesign(id= ~PPSU, 
                                   strata = ~PSTRAT, 
                                   nest = TRUE, 
                                   weights = ~wtfa, 
                                   data = NHIS_Child_Phase1)
```


**Household Pulse Survey**

```{r}
PulseSurvey_Wk1_Survey <- svydesign(id= ~PPSU, 
                                   strata = ~PSTRAT, 
                                   nest = TRUE, 
                                   weights = ~wtfa, 
                                   data = dfname)
```








```{r}
Redlining <- readRDS("Redlining.rds")
States <- readRDS("States_SpatialData.rds")
```

```{r}
table(Redlining$MAX_state)
northeast <- Redlining[Redlining@data$MAX_state %in% c( "MA", "RI", "CT", "NJ", "PA", "NY") , ]
```

```{r}
northeast_states <- States[States@data$STATE %in% c(25, 44, 09, 34, 42, 36 ) , ]
```



